Measuring Political Freedom Around the World

### 2020-11-03 slides.Rmd
added rmd template for slideshow

---
title: "Measuring Political Freedom Around the World"
author: " Joe Despres, Joe Sigler, Jacob Haywood, Sabrina Ball"
institute: "MSU"
date: "Updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

@@

```{r}
data <- read_csv(here::here("sttproj", "merged", "df.csv"))
```

```{r}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

>>>>

---
title: "Measuring Political Freedom Around the World"
subtitle: " Joe Despres, Joe Sigler, Jacob Haywood"
institute: "MSU"
date: "updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

@@

???
